Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-29 ba_resubmit/kundinger_resubmit3.tex
lots and lots of edits

\usepackage{lineno}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\newtheorem{lemma}{Lemma}
\usepackage{booktabs}       % professional-quality tables
\usepackage{algorithm}      % algorithm environment
\usepackage{algpseudocode}
\usepackage{subcaption}

@@

\begin{abstract} 
Within the field of record linkage, Bayesian methods have the crucial advantage of quantifying uncertainty from imperfect linkages. However, current implementations of Bayesian Fellegi-Sunter models are computationally intensive, making them challenging to use on larger-scale record linkage tasks. To address these computational considerations, we propose fast beta linkage (\texttt{fabl}), an extension to the Beta Record Linkage (\texttt{BRL}) method of \cite{sadinle_bayesian_2017}. Specifically, we use independent prior distributions over the matching space, allowing us to use hashing techniques that reduce computational overhead. This also allows us to complete pairwise record comparisons over large data files through parallel computing and to reduce memory costs through a new technique called storage efficient indexing. Through simulations and two case studies, we show that \texttt{fabl} can have markedly increased speed with minimal loss of accuracy when compared to \texttt{BRL}.
\end{abstract}

%\textcolor{teal}{which allows for parallel updates to the Gibbs sampler, contrasting the sequential updates of \texttt{BRL}.}
%\textcolor{teal}{We ensure our method is bipartite using decision theoretic post-processing techniques from the existing literature.}
%\textcolor{teal}{Next, we use hashing techniques that reduce computational overhead. Furthermore, we complete pairwise record comparisons over large data files through parallel computing and reduce memory costs through a new technique called storage efficient indexing. 
%}

%% ** Keywords **
\begin{keyword}
\kwd{bipartite record linkage}
\kwd{entity resolution}
\kwd{data cleaning}
\kwd{parallelization}
\kwd{hashing}
\end{keyword}

@@

Many probabilistic record linkage methods are rely on the seminal work of \cite{fellegi_theory_1969} and \cite{newcombe_automatic_1959}. In their approach, the data analyst first creates comparison vectors for each pair of records in the data files. These vectors indicate how similar the records are on a set of variables measured in both files, known as the linkage variables.  Using these comparison vectors, the analyst classifies each pair as a match or nonmatch using a likelihood ratio test. Crucially, these decisions are made independently for each pair. The \cite{fellegi_theory_1969} approach has been extended for a wide variety of applications \citep[e.g.,][]{Winkler1990, fair2004generalized, wagner2014person, gill2003english, enamorado2019using, aleshinguendel2021multifile}. An alternative paradigm is to model the linkage variables directly \citep[e.g.,][]{tancredi2011hierarchical, steorts_bayesian_2016, marchant_distributed_2019, betancourt2022prior}. In this article, we build on the contributions to the comparison vector approach.

The independent pairwise matching assumption from \cite{fellegi_theory_1969} is popular mainly for its mathematical simplicity. However, in many situations, there are no duplications within a data file, meaning that each record in one file should be linked with at most one other record in the other file. Thus, when the procedure results in many-to-one matches, some of these links must be false. To address this potential problem, data analysts typically use an additional post-processing step, for example, applying an optimization routine that turns the list of linked records into a bipartite matching \citep{jaro1989}.
%\textcolor{teal}{or using decision theoretic procedures, such as those of \cite{sadinle_bayesian_2017} and \cite{steorts_bayesian_2016}, which both ensure  bipartite (or rather transitive) matches.}

Alternatively, analysts can embed one-to-one matching requirements into the model specification, at an additional computational cost. \cite{Larsen05} employed a Metropolis-Hastings algorithm to only allow sampling matches that respected one-to-one assumptions, but such algorithms exhibit slow mixing due to the combinatorial nature of the constrained matching space. \cite{fortunato_2010} used simulated annealing to target the space of matches permitted under the one-to-one constraint, but the method is computationally intensive and, to our knowledge, has not been applied on data files with more than 100 records. \cite{sadinle_bayesian_2017} proposed the Beta Record Linkage model (\texttt{BRL}), using a prior distribution over the space of bipartite matchings to strictly enforce one-to-one requirements throughout a Gibbs sampler. Additionally, he introduced a class of loss functions that allows for a flexible estimation of the linkage structure, such that the modeler can weigh the relative importance of false positives and false negatives, and identify records pairings to be decided through clerical review. \texttt{BRL} has been shown to work on larger tasks than previous one-to-one methods, but in our experience, it becomes slow when applied to files with more than a few thousand records.

In this article, we propose fast beta linkage (\texttt{fabl}), which extends the \texttt{BRL} model for increased efficiency and scalability. {\color{red}{We use independent priors for the matching status of each record, inducing a dependency that is stronger than the record pair independence in the original \cite{fellegi_theory_1969} but weaker that the one-to-one requirement of \cite{sadinle_bayesian_2017}.}} \textcolor{teal}{This independence assumption allows for a scalable update of the Gibbs sampler, contrasting sequential updates of \cite{sadinle_bayesian_2017}. We employ the decision theoretic technique of \cite{sadinle_bayesian_2017} in order to ensure our method after record linkage is bipartite.}
This \textcolor{teal}{discovery} allows us to (1) employ hashing techniques that speed up calculations and reduce computational costs, (2) compute the pairwise record comparisons over large data files via parallel computing, and (3) reduce memory costs through what we call storage efficient indexing. These contributions allow \texttt{fabl} to perform record linkage on much larger data files than previous Bayesian Fellegi-Sunter models at significantly increased speed with similar levels of accuracy. In particular, computation time under \texttt{BRL} grows quadratically, with the size of each data file, while computation time under \texttt{fabl} grows linearly, only with the size of the smaller data file.

In what follows, Section \ref{sec:review-of_prior-work} reviews the work of \cite{fellegi_theory_1969} and \cite{sadinle_bayesian_2017}. Section \ref{sec:fast-beta-linkage} proposes the \texttt{fabl} model, provides the Gibbs sampler for posterior inference, and shows the loss function used to calculate the Bayes estimate for the bipartite matching. Section \ref{sec:efficiency} introduces the hashing technique and storage efficient indexing used to increase the speed of calculations and the scale of linkage tasks amenable to \texttt{fabl}. Sections \ref{sec:simulations} and \ref{sec:case-studies} demonstrate the speed and accuracy of \texttt{fabl} through simulation studies and case studies of homicides from the El Salvadoran Civil War and the National Long Term Care Study. Finally, Section \ref{discussion} summarizes our contributions and highlights areas for further research.

@@

Intuitively, matching records (those that refer to the same entity) should have similar values of the linking variables; records that are nonmatching should have dissimilar values. \cite{fellegi_theory_1969} proposed encoding this using a comparison vector $\gamma_{ij}$ computed for each record pair $(i,j)$ in $A \times B.$  Specifically, they define $\gamma_{ij} = (\gamma_{ij}^1, \ldots, \gamma_{ij}^F),$ where each $\gamma_{ij}^f$ is a value indicating the similarity of field $f$ for records $A_i$ and $B_j$. For notational convenience, we define the comparison matrix $\gamma \in \mathbb{R}^{n_A n_B F}$ as the collection of all record pairs' $\gamma_{ij}$.

@@

%\textcolor{red}{In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. 
%We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.}

@@

Let $\Gamma_{ij}$ represent a random variable for the comparison vector for arbitrary $A_i$ and $B_j$.  Thus, $\gamma_{ij}$ is a realization of $\Gamma_{ij}$.  For modeling the collection of $n_An_B$ random variables $\Gamma_{ij}$, \cite{fellegi_theory_1969} employ two independence assumptions: first, that comparison vectors are conditionally independent given their matching status, and second, that the matching status of the record pairs are independent. Using these independence assumptions,  one specifies a mixture model for each $\Gamma_{ij}$ \citep[e.g., as in ][]{winkler_state_1999,jaro1989,larsen_2001,enamorado2019using}.  We have
\begin{subequations}
\begin{align}
&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 1 \stackrel{iid}{\sim} \mathcal{M}(\bm{m}), \label{eqn:fs_model} \\
&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 0  \stackrel{iid}{\sim} \mathcal{U}(\bm{u}), \label{eqn:m_dist}\\
&\Delta_{ij}   \stackrel{iid}{\sim} \text{Bernoulli}(\lambda). \label{eqn:lambda_dist}
\end{align}
\end{subequations}
Here, $\mathcal{M}$ and $\mathcal{U}$ are the distributions for matching and nonmatching record pairs, $\bm{m}$ and $\bm{u}$ are their respective sets of parameters, and $\lambda$ is the marginal probability that a record pair is a match. When using comparison vectors with discrete agreement levels, $\mathcal{M}$ and $\mathcal{U}$ are collections of independent multinomial distributions for each linkage feature. Accordingly, $\bm{m} = (\bm{m}_1, \ldots, \bm{m}_F)$, where $\bm{m}_f = (m_{f1}, \ldots, m_{fL_f})$ and $m_{fl} = p(\gamma_{ij}^f = l|\Delta_{ij} = 1)$ for all fields $f$ and agreement levels $l$. The $\bm{u}$ parameters are defined similarly, with $u_{fl} = p(\gamma_{ij}^f = l|\Delta_{ij} = 0)$.

\cite{sadinle_bayesian_2017} presents a Bayesian version of the model in \eqref{eqn:fs_model} through \eqref{eqn:lambda_dist}.  He uses uniform Dirichlet prior distributions for each $\bm{m}_f$ and $\bm{u}_f$.  As the prior distriburion for  $\bm{Z}$, he proposes the ``beta distribution for bipartite matching."  This assigns a Bernoulli distribution for the indicator that a record in $B$ has a match in $A$, that is, $I(Z_j \leq n_A) \sim \text{Bernoulli}(\pi)$.  Additionally, $\pi \sim \text{Beta}(\alpha_{\pi}, \beta_{\pi})$, \textcolor{teal}{where  $\alpha_{\pi}, \beta_{\pi}$ are known hyper-parameters.}

It follows that the number of records in $B$ that have matches, denoted $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B} I(Z_j \leq n_A)$, is distributed according to a $\text{Beta-Binomial}(n_B, \alpha_{\pi}, \beta_{\pi})$. Conditioning on the set of records in $B$ that have matches, formally denoted $\{I(Z_j \leq n_A)\}_{j=1}^{n_B}$, all $n_A ! / (n_A - n_{AB}(\bm{Z}))!$ bipartite matchings are taken to be equally likely. Thus, the prior distribution used by \cite{sadinle_bayesian_2017} is given by
\begin{align}
\label{eqn:sadinle_prior}
p(\bm{Z}|\alpha_{\pi}, \beta_{\pi}) = \frac{(n_A - n_{AB}(\bm{Z}))!}{n_A !}\frac{\text{B}(n_{AB}(\bm{Z}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}) + \beta_{\pi})}{\text{B}(\alpha_{\pi}, \beta_{\pi})},
\end{align}
where $\text{B}(\cdot, \cdot)$ represents the Beta function. This prior strictly enforces one-to-one matching, inducing a Gibbs sampler that removes previously matched records from the set of candidate records when sampling each $Z_j$. This makes the sampler inherently \textcolor{teal}{sequential}, which can be slow when working on linkage tasks with more than a few thousand records.

@@

Instead of the prior over $\bm{Z}$ from \cite{sadinle_bayesian_2017}, we follow \cite{wortman2019} and use independent priors for each component $Z_j$. However, unlike \cite{wortman2019} who proposes a flat prior for $Z_j$, 
\textcolor{teal}{we propose an alternative, called the fast beta linkage (fabl) prior.}
%the fast Beta prior as follows. 
For each $Z_j$, we have
\begin{subequations}
\begin{align}
	p(Z_j = q| \pi) &= \begin{cases} 
	\frac{1}{n_A}\pi,  & q \leq n_A;\\
	1-\pi, &  q  = n_A + j;  \\
\end{cases} \label{eqn:fast_beta_prior}  \\
\pi &\sim \text{Beta}(\alpha_{\pi}, \beta_{\pi}) \label{eqn:fast_beta_prior2}.
\end{align}
\end{subequations}
We can interpret (\ref{eqn:fast_beta_prior}) as follows: record $B_j$ has some match in $A$ with probability $\pi$, and each record $A_i$ is equally likely to be that match. The hyperparameters $\alpha_{\pi}$ and $\beta_{\pi}$ encode prior beliefs about  the proportion of records in $B$ that have matches in $A.$

%\textcolor{red}{In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. 
%We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.}

\textcolor{teal}{We now explain how we accomodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing completely at random (MCAR, per \cite{LittleRubin2002}). With the MCAR assumption, we can marginalize over the missing data in (\ref{eqn:likelihood}), and do all computation simply using the observed data.}

%are ignorable (or random) \citep{LittleRubin2002}. The likelihood becomes that in (\ref{eqn:likelihood}), following directly from \cite{sadinle_bayesian_2017}. Note that both assumptions used here are for computational convenience. Missing completely at random (MCAR) applies when the probability that a value of a variable is missing does not depend on the observed or unobserved variables. Missing at random (MAR) is present when the probability of missingness depends only on (the values of other) observed variables.}
%\textcolor{red}{In Sadinle (2017), he assumes MAR and in the JASA paper he assumes ignorability.}

\textcolor{teal}{We summarize our proposed approach as follows:}

>>>>

\usepackage{afterpage}
\usepackage{lineno}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\newtheorem{lemma}{Lemma}
\usepackage{booktabs}       % professional-quality tables
\usepackage{algorithm}      % algorithm environment
\usepackage{algpseudocode}
\usepackage{subcaption}

@@

\begin{abstract}
%Recently, researchers have developed Bayesian versions of the Fellegi-Sunter model for record linkage. These have the crucial advantage of quantifying uncertainty from imperfect linkages.  
Within the field of record linkage, Bayesian methods have the crucial advantage of quantifying uncertainty from imperfect linkages. However, current implementations of Bayesian Fellegi-Sunter models are computationally intensive, making them challenging to use on larger-scale record linkage tasks. To address these computational difficulties, we propose fast beta linkage (\texttt{fabl}), an extension to the Beta Record Linkage (\texttt{BRL}) method of \cite{sadinle_bayesian_2017}. Specifically, we use independent prior distributions over the matching space, allowing us to use hashing techniques that reduce computational overhead. This also allows us to complete pairwise record comparisons over large data files through parallel computing and to reduce memory costs through a new technique called storage efficient indexing. Through simulations and two case studies, we show that \texttt{fabl} can have markedly increased speed with minimal loss of accuracy when compared to \texttt{BRL}.
%
%\textcolor{blue}{We propose a variation on Bayesian Fellegi-Sunter models that we call fast beta linkage, or \texttt{fabl}, and is motivated by computational considerations.  Our method extends that of \cite{sadinle_bayesian_2017}, who extended the early work of \cite{fellegi_theory_1969}.}

\end{abstract}

%% ** Keywords **
\begin{keyword}%[class=MSC]
\kwd{data fusion}
\kwd{distributed computing}
\kwd{entity resolution}
\kwd{hashing}
\kwd{record linkage}
\end{keyword}

@@

Many probabilistic record linkage methods rely on the seminal work of \cite{fellegi_theory_1969} and \cite{newcombe_automatic_1959}. In their approach, the data analyst first creates comparison vectors for each pair of records in the data files. These vectors indicate how similar the records are on a set of variables measured in both files, known as the linkage variables.  Using these comparison vectors, the analyst classifies each pair as a match or nonmatch using a likelihood ratio test. Crucially, these decisions are made independently for each pair. The \cite{fellegi_theory_1969} approach has been extended for a wide variety of applications \citep[e.g.,][]{Winkler1990, fair2004generalized, wagner2014person, gill2003english, enamorado2019using, aleshinguendel2021multifile}. An alternative paradigm is to model the linkage variables directly \citep[e.g.,][]{tancredi2011hierarchical, steorts_bayesian_2016, marchant_distributed_2019, betancourt2022prior}. In this article, we build on the contributions to the comparison vector approach.

% Possible citation for bipartite matching. 
%\citep{fellegi_theory_1969, jaro1989, Winkler1988, belin_A995, larsen_2001, liseo_2011,  herzog2007data, gutman_bayesian_2013, sadinle_bayesian_2017}.

The independent pairwise matching assumption from \cite{fellegi_theory_1969} is popular for its mathematical simplicity. However, in many situations, there are no duplications within a data file, meaning that each record in one file should be linked with at most one other record in the other file. Thus, when the procedure results in many-to-one matches, some of these links must be false. Analysts typically use an additional post-processing step to turn the list of linked records into a bipartite matching \citep{jaro1989}, but this model misspecification can still lead to poor results \citep{sadinle_bayesian_2017}.

Alternatively, analysts can embed one-to-one matching requirements into the model specification, at an additional computational cost. \cite{Larsen05} employed a Metropolis-Hastings algorithm to only allow sampling matches that respect one-to-one assumptions, but such algorithms exhibit slow mixing due to the combinatorial nature of the constrained matching space. \cite{fortunato_2010} used simulated annealing to target the space of matches permitted under the one-to-one constraint, but the method is computationally intensive and, to our knowledge, has not been applied on data files with more than 100 records. \cite{sadinle_bayesian_2017} proposed the Beta Record Linkage model (\texttt{BRL}), using a prior distribution over the space of bipartite matchings to strictly enforce one-to-one requirements throughout a Gibbs sampler. \texttt{BRL} has been shown to work on larger tasks than previous one-to-one methods, but in our experience, it becomes slow when applied to files with more than a few thousand records.

%Additionally, he introduced a class of loss functions that allows for a flexible estimation of the linkage structure, such that the modeler can weigh the relative importance of false positives and false negatives, and identify records pairings to be decided through clerical review.

In this article, we propose fast beta linkage (\texttt{fabl}), which extends the \texttt{BRL} model for increased efficiency and scalability. We use independent prior distributions for the matching statuses of each record, and modify the decision theoretic technique of \cite{sadinle_bayesian_2017} to ensure our linkage estimates are bipartite. This approach allows us to (1) employ hashing techniques that speed up calculations and reduce computational costs, (2) compute the pairwise record comparisons over large data files via parallel computing, and (3) reduce memory costs through what we call storage efficient indexing. These contributions allow \texttt{fabl} to perform record linkage on much larger data files than previous Bayesian Fellegi-Sunter models at significantly increased speed with similar levels of accuracy. In particular, computation time under \texttt{BRL} grows quadratically, with the size of each data file, while computation time under \texttt{fabl} grows linearly, only with the size of the smaller data file.

%

%{\color{red}{We use independent priors for the matching status of each record, inducing a dependency that is stronger than the record pair independence in the original \cite{fellegi_theory_1969} but weaker that the one-to-one requirement of \cite{sadinle_bayesian_2017}.}}

In what follows, Section \ref{sec:review-of_prior-work} reviews the work of \cite{fellegi_theory_1969} and \cite{sadinle_bayesian_2017}. Section \ref{sec:fast-beta-linkage} proposes the \texttt{fabl} model, provides the Gibbs sampler for posterior inference, and describes the loss function used to calculate the Bayes estimate for the bipartite matching. Section \ref{sec:efficiency} introduces the hashing technique and storage efficient indexing used to increase the speed of calculations and the scale of linkage tasks amenable to \texttt{fabl}. Sections \ref{sec:simulations} and \ref{sec:case-studies} demonstrate the speed and accuracy of \texttt{fabl} through simulation studies and case studies of homicides from the El Salvadoran Civil War and the National Long Term Care Study. Finally, Section \ref{discussion} summarizes our contributions and highlights areas for further research.

@@

%Consider two data files $A$ and $B$, consisting of records $\{A_i: i = 1, \ldots, n_A\}$ and $\{B_j: j = 1, \ldots, n_B\}$. Suppose the files have $F$ fields in common to be used for linkage, and that these fields take on values $A_{if}$ and $B_{jf}$ respectively.

Intuitively, matching records (those that refer to the same entity) should have similar values of the linking variables; records that are nonmatching should have dissimilar values. \cite{fellegi_theory_1969} proposed encoding this using a comparison vector $\gamma_{ij}$ computed for each record pair $(i,j)$ in $A \times B.$  Specifically, they define $\gamma_{ij} = (\gamma_{ij}^1, \ldots, \gamma_{ij}^F),$ where each $\gamma_{ij}^f$ is a value indicating the similarity of field $f$ for records $A_i$ and $B_j$. We define the comparison matrix $\gamma \in \mathbb{R}^{n_A n_B F}$ as the collection of all record pairs $\gamma_{ij}$. Additionally, we let $\Gamma_{ij}$ represent a random variable for the comparison vector for $A_i$ and $B_j$, such that $\gamma_{ij}$ is a realization of $\Gamma_{ij}$.

@@

In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.

%\subsection{Fellegi-Sunter Models}
%\label{fellegi-sunter}

@@

%Let $\Gamma_{ij}$ represent a random variable for the comparison vector for arbitrary $A_i$ and $B_j$.  Thus, $\gamma_{ij}$ is a realization of $\Gamma_{ij}$.

For modeling the collection of $n_An_B$ random variables $\Gamma_{ij}$, \cite{fellegi_theory_1969} employ two independence assumptions: first, that comparison vectors are conditionally independent given their matching status, and second, that the matching status of the record pairs are independent. Using these independence assumptions,  one specifies a mixture model for each $\Gamma_{ij}$ \citep[e.g., as in ][]{winkler_state_1999,jaro1989,larsen_2001,enamorado2019using}.  We have
\begin{subequations}
\begin{align}
&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 1 \stackrel{iid}{\sim} \mathcal{M}(\bm{m}), \label{eqn:fs_model} \\
&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 0  \stackrel{iid}{\sim} \mathcal{U}(\bm{u}), \label{eqn:m_dist}\\
&\Delta_{ij}   \stackrel{iid}{\sim} \text{Bernoulli}(\lambda). \label{eqn:lambda_dist}
\end{align}
\end{subequations}
Here, $\mathcal{M}$ and $\mathcal{U}$ are the distributions for matching and nonmatching record pairs, $\bm{m}$ and $\bm{u}$ are their respective sets of parameters, and $\lambda$ is the marginal probability that a record pair is a match. When using comparison vectors with discrete agreement levels, $\mathcal{M}$ and $\mathcal{U}$ are collections of independent multinomial distributions for each linkage feature. Accordingly, $\bm{m} = (\bm{m}_1, \ldots, \bm{m}_F)$, where $\bm{m}_f = (m_{f1}, \ldots, m_{fL_f})$ and $m_{fl} = p(\gamma_{ij}^f = l|\Delta_{ij} = 1)$ for all fields $f$ and agreement levels $l$. The $\bm{u}$ parameters are defined similarly, with $u_{fl} = p(\gamma_{ij}^f = l|\Delta_{ij} = 0)$.

%Within this framework, record pairs are independently classified as matches and nonmatches based on the estimated parameters. However, such independent classifications often leads to links that violate one-on-one matching assumptions, requiring post-processing to achieve desirable results. To address this issue, \cite{jaro1989} proposed an optimization technique using the estimated model parameters to produce a bipartite matching. \cite{sadinle_bayesian_2017} later showed that this method is equivalent to a maximum likelihood estimate.

%The Fellegi-Sunter method then uses thresholds $T_m$ and $T_u$ such that all record pairs with $w_{ij} > T_m$ are declared as links, and all those with $w_{ij} < T_u$ are declared as non-links (with those such that $T_u < w_{ij} < T_m$ left undetermined and subject to clerical review). This is a problem in practice as transitive closures can be violated. Since each $w_{ij}$ is calculated independently, there can be situations in which both $w_{ij} > T_m$ and $w_{i'j} > T_m$, so both $(i,j)$ and $(i', j)$ are declared as links, even though such a matching is not allowed by assumption.

%To address this issue, \cite{jaro1989} proposed solving the following linear sum assignment problem:
%\begin{align}
%     \label{eqn:jaro}
%     &\max_{\Delta} \sum_{i=1}^{n_A} \sum_{j=1}^{n_B} w_{ij} \Delta_{ij}
%     \quad \text{subject to} \quad \Delta_{ij} \in \{0,1\}; \\
%     & \quad \quad \sum_{i=1}^{n_A}  \Delta_{ij}  \leq 1, j=1,2, \ldots n_B; \; \text{and} \notag\\
%     & \quad \quad\sum_{i=1}^{n_B}  \Delta_{ij}  \leq 1, i=1,2, \ldots n_A. \notag
%\end{align}
%
%The solution to this problem, for which several simple algorithms exist, is a bipartite matching that maximizes the sum of the Fellegi-Sunter weights among matched pairs. Jaro provided no theoretical justification for using this approach; however \cite{sadinle_bayesian_2017} recently showed that under certain conditions, (\ref{eqn:jaro}) is the maximum likelihood estimate for bipartite matching.

%The comparison data $\gamma_{ij}$ are not sufficient to determine whether a record is a match or nonmatch because of errors that naturally occur in the data. This motivated \cite{fellegi_theory_1969} to consider the likelihood ratio
%\begin{align}
%     \label{eqn:wts}
%     w_{ij} = \frac{p(\gamma_{ij} \mid \Delta_{ij} = 1)}{p(\gamma_{ij} \mid \Delta_{ij} = 0)}
%\end{align}
%as a weight to estimate if record pairs are a match or nonmatch. This ratio will be large when there is strong evidence of the pair being a match, and small otherwise.
%
%In practice, $p(\cdot \mid \Delta_{ij} = 1)$ and $p(\cdot \mid \Delta_{ij} = 0)$ are unknown to the modeler, and thus must be estimated.
%
%%is the set of parameters $u_{fl} = p(\gamma_{ij}^f = l|Z_j \neq i)$ for the nonmatching pairs.
%
%After estimating $\bm{m}$ and $\bm{u}$, the Fellegi-Sunter method uses thresholds $T_m$ and $T_u$ such that all record pairs with $w_{ij} > T_m$ are declared as links, and all those with $w_{ij} < T_u$ are declared as non-links (with those such that $T_u < w_{ij} < T_m$ left undetermined and subject to clerical review). This is a problem in practice as transitive closures can be violated. Since each $w_{ij}$ is calculated independently, there can be situations in which both $w_{ij} > T_m$ and $w_{i'j} > T_m$, so both $(i,j)$ and $(i, j')$ are declared as links, even though such a matching is not allowed by assumption.

%\subsection{Beta Record Linkage Model}
%\label{BRL}

%To estimate a one-to-one matching without using a post-processing step, \cite{sadinle_bayesian_2017} incorporated this constraint directly into the model through a prior distribution over the matching space.

%To estimate a one-to-one matching without using a post-processing step, \cite{sadinle_bayesian_2017} incorporates this constraint directly into the model through a

\cite{sadinle_bayesian_2017} presents a Bayesian version of the model in \eqref{eqn:fs_model} through \eqref{eqn:lambda_dist}.  He uses uniform Dirichlet prior distributions for each $\bm{m}_f$ and $\bm{u}_f$, and replaces (\ref{eqn:lambda_dist}) with a prior distribution for $\bm{Z}$ that he calls the ``beta distribution for bipartite matching."  This assigns a Bernoulli distribution for the indicator that a record in $B$ has a match in $A$, that is, $I(Z_j \leq n_A) \sim \text{Bernoulli}(\pi)$.  Additionally, $\pi \sim \text{Beta}(\alpha_{\pi}, \beta_{\pi})$, where $\alpha_{\pi}$ and $\beta_{\pi}$ are known hyperparameters. It follows that the number of records in $B$ that have matches, denoted $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B} I(Z_j \leq n_A)$, is distributed according to a $\text{Beta-Binomial}(n_B, \alpha_{\pi}, \beta_{\pi})$. Conditioning on the set of records in $B$ that have matches, formally denoted $\{I(Z_j \leq n_A)\}_{j=1}^{n_B}$, all $n_A ! / (n_A - n_{AB}(\bm{Z}))!$ bipartite matchings are taken to be equally likely. Thus, the prior distribution used by \cite{sadinle_bayesian_2017} is given by
\begin{align}
\label{eqn:sadinle_prior}
p(\bm{Z}|\alpha_{\pi}, \beta_{\pi}) = \frac{(n_A - n_{AB}(\bm{Z}))!}{n_A !}\frac{\text{B}(n_{AB}(\bm{Z}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}) + \beta_{\pi})}{\text{B}(\alpha_{\pi}, \beta_{\pi})},
\end{align}
where $\text{B}(\cdot, \cdot)$ represents the Beta function. This prior strictly enforces one-to-one matching, inducing a Gibbs sampler that removes previously matched records from the set of candidate records when sampling each $Z_j$. This makes the sampler inherently sequential, which can be slow when working on linkage tasks with more than a few thousand records.

@@

Instead of the prior over $\bm{Z}$ from \cite{sadinle_bayesian_2017}, we follow \cite{wortman2019} and use independent priors for each component $Z_j$. However, unlike \cite{wortman2019} who proposes a flat prior for $Z_j$, we use the fast Beta linkage (\texttt{fabl}) prior below. For each $Z_j$, we have
%\begin{subequations}
\begin{align}
	p(Z_j = q| \pi) &= \begin{cases} 
	\frac{1}{n_A}\pi,  & q \leq n_A;\\
	1-\pi, &  q  = n_A + j;  \\
\end{cases} \label{eqn:fast_beta_prior}  \\
\pi &\sim \text{Beta}(\alpha_{\pi}, \beta_{\pi}) \nonumber
%\label{eqn:fast_beta_prior2}.
\end{align}
%\end{subequations}
We can interpret (\ref{eqn:fast_beta_prior}) as follows: record $B_j$ has some match in $A$ with probability $\pi$, and each record $A_i$ is equally likely to be that match. The hyperparameters $\alpha_{\pi}$ and $\beta_{\pi}$ encode prior beliefs about  the proportion of records in $B$ that have matches in $A.$

In the \cite{wortman2019} flat prior, each value $\{1, \ldots, n_A, n_A +j\}$ is a priori equally likely for $Z_j$. This amounts to a prior probability of $n_A / (n_A + 1)$ that record $B_j$ has a match in $A$. In our preliminary studies, this highly informative prior weighting on matching can result in overly high match rates. Hence, we prefer (\ref{eqn:fast_beta_prior}). We also note that the flat prior is equivalent to a special case of the fast Beta prior with $\pi$ fixed at the mean of a $\text{Beta}\left(1, 1 / n_A \right)$ random variable.

Linkage with \texttt{fabl} is conducted at the record level, rather than at the record pair level, as in the \cite{fellegi_theory_1969} model. That is, $\pi$  in (\ref{eqn:fast_beta_prior}) under \texttt{fabl} estimates the proportion of records in $B$ that have matches, whereas $\lambda$ in (\ref{eqn:lambda_dist}) in the \cite{fellegi_theory_1969} model estimates the proportion of record pairs that are matches. In the bipartite case, we conjecture that some analysts will find $\pi$ to be more a interpretable parameter than $\lambda$. In this setting, there are at most $n_B$ matching pairs out of $n_A n_B$ total pairs, meaning that $\lambda$ is bounded above by $1/n_A$ and tends towards 0 as the size of the linkage task grows. Additionally, while the \cite{fellegi_theory_1969} model makes $n_A  n_B$ independent matching decisions and \texttt{BRL} makes $n_B$ dependent matching decisions, \texttt{fabl} strikes a middle ground between the two, making $n_B$  independent matching decisions. As shown in Sections \ref{sec:simulations} and \ref{sec:case-studies}, this allows \texttt{fabl} to fit a Bayesian record linkage model like \texttt{BRL} while making computational efficiency gains possible by exploiting independence.
